Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2019-01-13 paper/ijm.tex
Minor changes for the article proof

%\documentclass[10pt,a4paper,english]{article}
\documentclass[12pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
\usepackage[english]{babel}
%\usepackage{lmodern}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage[official]{eurosym}
\setcounter{secnumdepth}{3}

@@

\usepackage[format=hang, justification=RaggedRight]{caption}
\usepackage[section]{placeins}
\usepackage{float}
\usepackage{booktabs}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage[layout=margin,author=,status=draft]{fixme}
 \usepackage[final]{changes} %Manually track changes
 \definechangesauthor{SKB}
\usepackage{longtable}
\usepackage{paralist}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[natbibapa]{apacite}
%\usepackage[authoryear]{natbib}
\usepackage{csquotes}
%modifying the thanks commands
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black]{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}

\DeclareUnicodeCharacter{2010}{-}% support older LaTeX versions
\thanksfootextra{}{\hfill}
\setlength{\thanksmargin}{1em}
\setlength{\thanksmarkwidth}{0.75em}

\fxsetup{theme=color}
%Custom commands
\newcommand{\eur}{\EUR}
\newcommand{\std}[1]{\emph{(#1)}}
\newcommand{\V}{\checkmark}
\def\fns{\footnotesize}
\renewcommand*{\vec}[1]{\boldsymbol{#1}}

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} % needed for the tables produced by the esttab command in Stata, to avoid redundancy put here instead of in appendix.tex, where it is needed		
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies}
\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

%\maketitle
%\begin{center}
%	\textbf{{\large Language Skills in an Ethnically Segmented Labour market:
%				Estonia 1989 -- 2012}} \\
%	{\large Sven-Kristjan Bormann} \\
%	\emph{School of Economics and Business Administration, University of Tartu, Narva mnt. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
%
%	{\large Svetlana Ridala} \\
%	\emph{School of Business and Governance, Tallinn University of Technology, Akadeemia tee 3, 12618 Tallinn, Estonia\\ Email: \href{
%			mailto:svetlana.ridala@gmail.com}{
%			svetlana.ridala@gmail.com}} \\
%		{\large Ott Toomet}\\
%		\emph{Information School, University of Washington, USA; Email: \href{mailto:otoomet@uw.edu}{otoomet@uw.edu}}
%%	\emph{(Received XX XXXX 20XX; accepted XX XXXX 20XX)}\\
%	\textbf{Corresponding author:} Sven-Kristjan Bormann Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}
%\end{center}
%\paragraph{Short biographical note:} \hspace{0pt} \\
%Sven-Kristjan Bormann born 28.11.1985, graduated in 2011 from Kiel University, Germany in Economics with specialisation in Quantitative Economics and Computer Science. Since September 2012 PhD-student in Economics at Tartu University, Estonia. \\
%Svetlana Ridala born 28.03.1976, graduated in 2003 from Tallinn Pedagogical University, Estonia master's (scien) degree in mathematics. Since 2009 PhD-student in Economics at Tallinn School of Economics and Business Administration, Estonia.
%\\
%Ott-Siim Toomet born 18.03.1970, graduated in 2004 from Aarhus University, Denmark PhD in Economics. Since 2015 Visiting scholar, Information School, University of Washington.
%
%\paragraph{Research funding}
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.
%\newpage
%\noindent
{\centering \textbf{Language Skills in an Ethnically Segmented Labour Market: Estonia 1989 -- 2012}}
\begin{abstract}
 \noindent
 \textbf{Purpose --} We analyse the relationship between skills in the
 Estonian, Russian and English language, and labour market
 outcomes in Estonia, a linguistically divided country.
 \\
 \textbf{Design/methodology/approach --} We use the Estonian Labour
 Force Surveys 1992--2012. We rely on multivariate linear regression
 models to document the relationship between language skills and
 labour market outcomes.
 \\
 \textbf{Findings --} Estonian language knowledge (for ethnic Russians)
 are important determinants of unemployment. Wage, in contrary, is
 closely related to English skills. Ethnic Russian men do not earn
 any premium from speaking Estonian, while women, fluent in Estonian
 earn approximately 10\% more. For ethnic Estonians, Russian fluency
 is associated with a similar income gain.
 \\
 \textbf{Research limitations/implications -- } Due to the
 observational nature of the data, the effects reported in our study
 are not causal effects. As a second limitation, the self-reported
 language skills data may be imprecise and hence the effects we
 report may be too small.
 \\
 \textbf{Practical implications --} Our results stress the role of
 workplace segregation, both along gender and ethnic lines, in
 determining the individual labour market experience. 
 \\
 \textbf{Originality/value --} We provide a comprehensive overview of
 the effects of language skills in a rapidly developing labour
 market in a linguistically divided economy. We analyse several
 languages with different legal status and document long-term
 trends in the effects.
 \\
\end{abstract}
\textbf{Keywords:} language skills, ethnicity, wage gap, unemployment, Estonia \\
\textbf{JEL classification:} J15, J31, J71

@@

% Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
\begin{sidewaystable}[htbp]
	\centering
	\caption{Averages and relative frequencies of selected explanatory
		variables 2000 -- 2012}
	\begin{tabular}{l|rrrr|rrrr}
		\toprule
		& \multicolumn{4}{c|}{Estonians}  &  \multicolumn{4}{c}{Russians}  \\ \midrule
		Variable          & RUS 0 & RUS 1 & ENG 0 & ENG 1 & EST 0 & EST 1 & ENG 0 & ENG 1 \\ \midrule
		Wage, men (EUR)       & 543.86 & 537.22 & 438.53 & 738.63 & 401.59 & 489.96 & 388.91 & 660.39 \\
		Wage, women (EUR)      & 345.51 & 376.98 & 301.13 & 488.83 & 238.25 & 338.62 & 266.87 & 435.60 \\
		Unemployment (\%)      & 8.74  & 7.13  & 8.83  & 4.99  & 17.30 & 11.18 & 15.06 & 11.23 \\
		EST 1 (\%)         & 99.97 & 99.58 & 99.50 & 99.95 & 0.00  & 100.00 & 40.84 & 80.97 \\
		RUS 1 (\%)         & 0.00  & 100.00 & 77.35 & 82.86 & 99.90 & 99.04 & 99.65 & 98.77 \\
		ENG 1 (\%)         & 29.47 & 37.16 & 0.00  & 100.00 & 6.70  & 30.69 & 0.00  & 100.00 \\
		College Degree (\%)     & 15.61 & 23.44 & 10.77 & 41.38 & 12.66 & 28.64 & 13.93 & 49.16 \\
		Married (\%)        & 40.09 & 55.71 & 54.11 & 49.53 & 63.54 & 60.78 & 63.38 & 56.99 \\
		Inter-ethnic household (\%) & 1.34  & 5.20  & 4.79  & 3.70  & 5.07  & 19.46 & 11.97 & 12.17 \\
		Age             & 37.05 & 41.83 & 42.39 & 38.05 & 42.14 & 40.54 & 42.15 & 37.83 \\
		Kids (number)        & 1.08  & 1.00  & 1.00  & 1.00  & 0.71  & 0.76  & 0.75  & 0.68  \\
		\textbf{Residence County } &    &    &    &    &    &    &    &    \\
		Metropolitan (\%)      & 17.74 & 22.58 & 14.03 & 35.25 & 35.43 & 56.37 & 38.82 & 75.50 \\
		North-East (\%)       & 0.64  & 3.14  & 3.46  & 1.10  & 53.84 & 15.85 & 40.90 & 11.54 \\
		\textbf{Workplace}     &    &    &    &    &    &    &    &    \\
		Tenure (years)       & 6.17  & 7.33  & 7.45  & 6.40  & 8.19  & 7.23  & 8.08  & 5.99  \\
		Public sector (\%)     & 20.03 & 24.81 & 21.79 & 27.55 & 11.62 & 21.67 & 16.28 & 18.14 \\
		Primary sector (\%)     & 14.10 & 9.80  & 13.00 & 6.43  & 9.91  & 7.46  & 8.82  & 8.11  \\
		Secondary sector (\%)    & 31.02 & 27.20 & 32.63 & 19.41 & 47.21 & 29.72 & 41.54 & 24.07 \\
		Tertiary sector (\%)    & 26.17 & 30.12 & 26.52 & 34.46 & 27.17 & 33.96 & 28.37 & 40.96 \\
		\# Observations       & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862 \\ \bottomrule
	\end{tabular}%
	\label{tab:descriptive}%

@@

The central results for unemployment regressions are presented in
\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
 restrict both models to have the same number of observations as
 requested by a reviewer. The unrestricted results are provided in the Appendix (\Cref{tab:unemployment_estimation_by_sex_and_ethnic}).}.
The
table clearly indicates that Estonian language skills are associated
with an approximately 5 percentage points lower unemployment for both
Russian men and women. We also see that the effect is not 
influenced in any major way by the individual characteristics-- for men it is
virtually unchanged while for women the estimate falls by 30\%, from
6.5 to 4.5 percentage points.

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&     \multicolumn{2}{c}{Men}     &    \multicolumn{2}{c}{Women}    \\
			Estonians:   & \multicolumn{1}{c}{1}   & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}   & \multicolumn{1}{c}{2}   \\ \midrule
			Russian     & -0.026^{***}        & -0.001               & -0.009^{*}         & 0.010^{**}         \\
			        & (0.006)          & (0.006)              & (0.005)          & (0.005)          \\
			English     & -0.047^{***}        & -0.019^{***}            & -0.024^{***}        & -0.008^{*}         \\
			        & (0.004)          & (0.005)              & (0.004)          & (0.004)          \\
			\# Observations     & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}     & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$     & 0.022           & 0.047               & 0.012           & 0.036           \\ \hline
			Russians: & \\
			Estonian    & -0.052^{***}        & -0.052^{***}            & -0.065^{***}        & -0.045^{***}        \\
			        & (0.010)          & (0.011)              & (0.009)          & (0.010)          \\
			English     & -0.020          & 0.006               & -0.014           & -0.003           \\
			        & (0.012)          & (0.014)              & (0.011)          & (0.012)          \\
			\# Observations     & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}     & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$     & 0.033           & 0.066               & 0.023           & 0.043           \\ \hline
			year dummies  & \V             & \V                 & \V             & \V             \\
			indiv. charact. &              & \V                 &              & \V             \\
			\bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses; \\  Individual characteristics are \modelTwo.  \restrictions }
		\end{flushleft}
	\end{center}
\end{table}%

@@

\subsection{Wage}
%SKB: Adding occupation to Model 3 reduces the effects drastically. Beforehand I somehow forgot to add it to the estimation. Now occupation is included as it should have been in the first place.
\label{subsec:basic_model_wage}

@@

% latex table generated in R 3.4.4 by xtable 1.8-2 package
% Fri Jul 6 15:59:47 2018
\begin{table}[ht]
 \centering
 \caption{Average wage and time-trend corrected residual across
  location and education groups for Russian men}
 \begin{tabular}{llrrrr}
  \toprule
  & & &\multicolumn{2}{c}{Log Wage}\\
  Location & Education & \# Observations & EST 0 & EST 1 & Premium\\
  \midrule
  Tallinn & $<$ HS & 399 & -0.20 & -0.01 & 0.19 \\ 
  Tallinn & HS & 2,164 & 0.07 & 0.04 & -0.03 \\ 
  Tallinn & College Degree & 610 & 0.15 & 0.30 & 0.15 \\ 
  Other & $<$ HS & 501 & -0.12 & -0.12 & -0.01 \\ 
  Other & HS & 2,658 & -0.10 & -0.07 & 0.03 \\ 
  Other & College Degree & 429 & 0.17 & 0.11 & -0.06 \\ 
  \bottomrule
 \end{tabular}
 \begin{flushleft}
  Notes: \emph{Log Wage} refers to regression residual where log
  wage is explained by year fixed effects. \emph{EST 0} and
  \emph{EST 1} are mean values for those who cannot, and who can,
  speak Estonian; $\text{Premium} = \text{EST 1} - \text{EST 0}$.
  Education level \emph{< HS} refers to less than high school
  degree, \emph{HS} is the high school degree as the highest
  completed education.
 \end{flushleft}
 \label{tab:loc-lang-edu}
\end{table}

>>>>

\documentclass[12pt, a4paper,english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[hmargin=2.5cm,top=2.5cm, bottom=2.0cm]{geometry}
\usepackage{babel}
%\usepackage{lmodern}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage[official]{eurosym}
\setcounter{secnumdepth}{3}

@@

\usepackage[format=hang, justification=RaggedRight]{caption}
\usepackage[section]{placeins}
\usepackage{float}
\usepackage{booktabs}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{longtable}
\usepackage{paralist}
\usepackage{rotating}
\usepackage{subfigure}
\usepackage[natbibapa]{apacite}

\usepackage{csquotes}
%modifying the thanks commands
\usepackage{titling}
\usepackage[colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black]{hyperref}
\usepackage[noabbrev,capitalise]{cleveref}

%\DeclareUnicodeCharacter{2010}{-}% support older LaTeX versions
\thanksfootextra{}{\hfill}
\setlength{\thanksmargin}{1em}
\setlength{\thanksmarkwidth}{0.75em}

%Custom commands
\newcommand{\eur}{\EUR}
\newcommand{\std}[1]{\emph{(#1)}}
\newcommand{\V}{\checkmark}
\def\fns{\footnotesize}
\renewcommand*{\vec}[1]{\boldsymbol{#1}}
%\section{Own commands}
\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
\def\sym#1{\ifmmode^{#1}\else\(^{#1}\)\fi} 
%Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\industry}{Industry categories (according to NACE Rev.2): A Agriculture, Forestry and Fishing; B Mining and Quarrying; C Manufacturing; D Electricity, Gas, Steam and Air Conditioning Supply; E Water Supply;  Sewerage, Waste Management and Remediation Activities; F Construction; G Wholesale and Retail Trade;  Repair of Motor Vehicles and Motorcycles; H Transportation and Storage; I Accommodation and Food Service Activities; J Information and Communication; K Financial and Insurance Activities; L Real Estate Activities; M Professional, Scientific and Technical Activities; N Administrative and Support Service Activities; O Public Administration and Defence;  Compulsory Social Security; P Education; Q Human Health and Social Work Activities; R Arts, Entertainment and Recreation; S Other Service Activities; T Activities of Households as Employers;  Undifferentiate Goods and Services Producing Activities of Households for Own Use; U Activities of Extraterritorial Organisations and Bodies \\ }
\newcommand{\occupation}{Occupation categories according to ISCO-08: 1 Managers; 2 Professional; 3 Technicians and associate professionals; 4 Clerical support workers; 5 Service and sales workers; 6 Skilled agricultural, forestry and fishery workers; 7 Craft and related trades workers; 8 Plant and machine operators, and assemblers; 9 Elementary occupations; 10 Armed forces occupations \\ }
\newcommand{\ownership}{Ownership types: 10 -- government (Estonian State);
	20 -- local government;
	30 -- private, Estonian;
	40 -- private, foreign;
	50 -- private, mixed Estonian and foreign;
	90 -- other}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons 25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

%\maketitle
%\begin{center}
%	\textbf{{\large Language Skills in an Ethnically Segmented Labour market:
%				Estonia 1989 -- 2012}} \\
%	{\large Sven-Kristjan Bormann} \\
%	\emph{School of Economics and Business Administration, University of Tartu, Liivi. 4, 51007 Tartu, Estonia\\ Tel.: +372 5844 3873\\ Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}}	\\
%
%	{\large Svetlana Ridala} \\
%	\emph{School of Business and Governance, Tallinn University of Technology, Akadeemia tee 3, 12618 Tallinn, Estonia\\ Email: \href{
%			mailto:svetlana.ridala@gmail.com}{
%			svetlana.ridala@gmail.com}} \\
%		{\large Ott Toomet}\\
%		\emph{Information School, University of Washington, USA; Email: \href{mailto:otoomet@uw.edu}{otoomet@uw.edu}}
%%	\emph{(Received XX XXXX 20XX; accepted XX XXXX 20XX)}\\
%	\textbf{Corresponding author:} Sven-Kristjan Bormann Email: \href{mailto:bormann@ut.ee}{bormann@ut.ee}
%\end{center}
%\paragraph{Short biographical note:} \hspace{0pt} \\
%Sven-Kristjan Bormann born 28.11.1985, graduated in 2011 from Kiel University, Germany in Economics with specialisation in Quantitative Economics and Computer Science. Since September 2012 PhD-student in Economics at Tartu University, Estonia. \\
%Svetlana Ridala born 28.03.1976, graduated in 2003 from Tallinn Pedagogical University, Estonia master's (scien) degree in mathematics. Since 2009 PhD-student in Economics at Tallinn School of Economics and Business Administration, Estonia.
%\\
%Ott-Siim Toomet born 18.03.1970, graduated in 2004 from Aarhus University, Denmark PhD in Economics. Since 2015 Visiting scholar, Information School, University of Washington.
%
%\paragraph{Research funding}
%This research was supported by European Social Fund's Doctoral Studies
%and Internationalisation Program DoRa through Archimedes Foundation, and the Estonian Science Foundation grant 8627.
%\newpage
%\noindent
{\centering \textbf{Language Skills in an Ethnically Segmented Labour Market: Estonia 1989 -- 2012}}
\begin{abstract}
 \noindent
 \textbf{Purpose --} We analyse the relationship between skills in the
 Estonian, Russian and English language, and labour market
 outcomes in Estonia, a linguistically divided country.
 \\
 \textbf{Design/methodology/approach --} We use the Estonian Labour
 Force Surveys 1992--2012. We rely on multivariate linear regression
 models to document the relationship between language skills and
 labour market outcomes.
 \\
 \textbf{Findings --} Estonian language knowledge (for ethnic Russians)
 are important determinants of unemployment. Wage, in contrary, is
 closely related to English skills. Ethnic Russian men do not earn
 any premium from speaking Estonian, while women, fluent in Estonian
 earn approximately 10\% more. For ethnic Estonians, Russian fluency
 is associated with a similar income gain.
 \\
 \textbf{Research limitations/implications -- } Due to the
 observational nature of the data, the effects reported in our study
 are not causal effects. As a second limitation, the self-reported
 language skills data may be imprecise and hence the effects we
 report may be too small.
 \\
 \textbf{Practical implications --} Our results stress the role of
 workplace segregation, both along gender and ethnic lines, in
 determining the individual labour market experience. 
 \\
 \textbf{Originality/value --} We provide a comprehensive overview of
 the effects of language skills in a rapidly developing labour
 market in a linguistically divided economy. We analyse several
 languages with different legal status and document long-term
 trends in the effects.
 \\
\end{abstract}
\textbf{Keywords:} language skills, ethnicity, wage gap, unemployment, Estonia \\
\textbf{JEL classification:} J15, J31, J71

@@

\begin{sidewaystable}[htbp]
	\centering

	\caption{Averages and relative frequencies of selected explanatory
		variables 2000 -- 2012}
	\begin{tabular}{l|rrrr|rrrr}
		\toprule
		& \multicolumn{4}{c|}{Estonians}  &  \multicolumn{4}{c}{Russians}  \\ \midrule
		Variable          & RUS 0 & RUS 1 & ENG 0 & ENG 1 & EST 0 & EST 1 & ENG 0 & ENG 1 \\ \midrule
		Wage, men (EUR)       & 543.86 & 537.22 & 438.53 & 738.63 & 401.59 & 489.96 & 388.91 & 660.39 \\
		Wage, women (EUR)      & 345.51 & 376.98 & 301.13 & 488.83 & 238.25 & 338.62 & 266.87 & 435.60 \\
		Unemployment (\%)      & 8.74  & 7.13  & 8.83  & 4.99  & 17.30 & 11.18 & 15.06 & 11.23 \\
		EST 1 (\%)         & 99.97 & 99.58 & 99.50 & 99.95 & 0.00  & 100.00 & 40.84 & 80.97 \\
		RUS 1 (\%)         & 0.00  & 100.00 & 77.35 & 82.86 & 99.90 & 99.04 & 99.65 & 98.77 \\
		ENG 1 (\%)         & 29.47 & 37.16 & 0.00  & 100.00 & 6.70  & 30.69 & 0.00  & 100.00 \\
		College Degree (\%)     & 15.61 & 23.44 & 10.77 & 41.38 & 12.66 & 28.64 & 13.93 & 49.16 \\
		Married (\%)        & 40.09 & 55.71 & 54.11 & 49.53 & 63.54 & 60.78 & 63.38 & 56.99 \\
		Inter-ethnic household (\%) & 1.34  & 5.20  & 4.79  & 3.70  & 5.07  & 19.46 & 11.97 & 12.17 \\
		Age             & 37.05 & 41.83 & 42.39 & 38.05 & 42.14 & 40.54 & 42.15 & 37.83 \\
		Kids (number)        & 1.08  & 1.00  & 1.00  & 1.00  & 0.71  & 0.76  & 0.75  & 0.68  \\
		\textbf{Residence County } &    &    &    &    &    &    &    &    \\
		Metropolitan (\%)      & 17.74 & 22.58 & 14.03 & 35.25 & 35.43 & 56.37 & 38.82 & 75.50 \\
		North-East (\%)       & 0.64  & 3.14  & 3.46  & 1.10  & 53.84 & 15.85 & 40.90 & 11.54 \\
		\textbf{Workplace}     &    &    &    &    &    &    &    &    \\
		Tenure (years)       & 6.17  & 7.33  & 7.45  & 6.40  & 8.19  & 7.23  & 8.08  & 5.99  \\
		Public sector (\%)     & 20.03 & 24.81 & 21.79 & 27.55 & 11.62 & 21.67 & 16.28 & 18.14 \\
		Primary sector (\%)     & 14.10 & 9.80  & 13.00 & 6.43  & 9.91  & 7.46  & 8.82  & 8.11  \\
		Secondary sector (\%)    & 31.02 & 27.20 & 32.63 & 19.41 & 47.21 & 29.72 & 41.54 & 24.07 \\
		Tertiary sector (\%)    & 26.17 & 30.12 & 26.52 & 34.46 & 27.17 & 33.96 & 28.37 & 40.96 \\
		\# Observations       & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862 \\ \bottomrule
	\end{tabular}%
	\label{tab:descriptive}%

@@

The central results for unemployment regressions are presented in
\cref{tab:unemployment_estimation_by_sex_and_ethnic_same_sample}\footnote{We
 restrict both models to have the same number of observations as
 requested by a reviewer. The unrestricted results are provided in the Appendix (\Cref{tab:unemployment_estimation_by_sex_and_ethnic}).}.
The
table clearly indicates that Estonian language skills are associated
with an approximately 5 percentage points lower unemployment for both
Russian men and women. We also see that the effect is not 
influenced in any major way by the individual characteristics. For men it is
virtually unchanged while for women the estimate falls by 30\%, from
6.5 to 4.5 percentage points.

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} 
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&     \multicolumn{2}{c}{Men}     &    \multicolumn{2}{c}{Women}    \\
			Estonians:   & \multicolumn{1}{c}{1}   & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}   & \multicolumn{1}{c}{2}   \\ \midrule
			Russian     & -0.026^{***}        & -0.001               & -0.009^{*}         & 0.010^{**}         \\
			        & (0.006)          & (0.006)              & (0.005)          & (0.005)          \\
			English     & -0.047^{***}        & -0.019^{***}            & -0.024^{***}        & -0.008^{*}         \\
			        & (0.004)          & (0.005)              & (0.004)          & (0.004)          \\
			\# Observations     & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}     & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$     & 0.022           & 0.047               & 0.012           & 0.036           \\ \hline
			Russians: & \\
			Estonian    & -0.052^{***}        & -0.052^{***}            & -0.065^{***}        & -0.045^{***}        \\
			        & (0.010)          & (0.011)              & (0.009)          & (0.010)          \\
			English     & -0.020          & 0.006               & -0.014           & -0.003           \\
			        & (0.012)          & (0.014)              & (0.011)          & (0.012)          \\
			\# Observations     & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}     & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$     & 0.033           & 0.066               & 0.023           & 0.043           \\ \hline
			year dummies  & \V             & \V                 & \V             & \V             \\
			indiv. charact. &              & \V                 &              & \V             \\
			\bottomrule
		\end{tabular}
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses; \\  Individual characteristics are \modelTwo.  \restrictions }
		\end{flushleft}
	\end{center}
\end{table}%

@@

\subsection{Wage}
\label{subsec:basic_model_wage}

@@

\begin{table}[ht]
 \centering
 \caption{Average wage and time-trend corrected residual across
  location and education groups for Russian men}
 \begin{tabular}{llrrrr}
  \toprule
  & & &\multicolumn{2}{c}{Log Wage}\\
  Location & Education & \# Observations & EST 0 & EST 1 & Premium\\
  \midrule
  Tallinn & $<$ HS & 399 & -0.20 & -0.01 & 0.19 \\ 
  Tallinn & HS & 2,164 & 0.07 & 0.04 & -0.03 \\ 
  Tallinn & College Degree & 610 & 0.15 & 0.30 & 0.15 \\ 
  Other & $<$ HS & 501 & -0.12 & -0.12 & -0.01 \\ 
  Other & HS & 2,658 & -0.10 & -0.07 & 0.03 \\ 
  Other & College Degree & 429 & 0.17 & 0.11 & -0.06 \\ 
  \bottomrule
 \end{tabular}
 \begin{flushleft}
  Notes: \emph{Log Wage} refers to regression residual where log
  wage is explained by year fixed effects. \emph{EST 0} and
  \emph{EST 1} are mean values for those who cannot, and who can,
  speak Estonian; $\text{Premium} = \text{EST 1} - \text{EST 0}$.
  Education level \emph{< HS} refers to less than high school
  degree, \emph{HS} is the high school degree as the highest
  completed education.
 \end{flushleft}
 \label{tab:loc-lang-edu}
\end{table}
